### 2018-04-18 Old/paper_min.tex
Moving PhD paper from Dropbox to github.

We further modify the allocation rule in \cite{tuffin} in order to suit our
model. We argue that as there is no capacity bottleneck in our network as in
\cite{lazar} and \cite{semret}, we are able to increase the bid quantity and
take the maximum of the allocation rule. 
We will introduce a player type called an \emph{opt-out buyer} in order to perform our analysis. The
opt-out buyer maximizes its utility by placing bids with all sellers who are
able to fully meet their data requirements, similar to \cite{zheng}. 
We propose a \emph{data allocation rule},
{
\proposition{(Data allocation rule)}\label{allocation}
\begin{equation}
    a_i(s) = \max\big\lbrace d_i, \frac{d_i}{\sum_{k:p_k=p_i}d_k}
D_i(p_i,s_{-i})\big\rbrace
\end{equation}
}
The modified allocation rule changes the market dynamics by adding a threshold
to buyer behavior; the strategy is now to submit bids to a subset of
players, rather than incuding an assumption that data infinitely divisibile.

(NOTE: move this?)
We extend the P2P rules as in \cite{semret} to include a \emph{local} market
price function as determined by the subset of nodes participating in the
auction. Therefore the influence of the greater market on the individual
auctions will be influenced only by the submission of bids from buyers to
sellers. As a buyer may have access to multiple auctions, the sellers will be
dynamically influenced by the $\epsilon$-best replies from the buyers. The
valuation function of seller $j$ is dependent on the buyers demand, and can be
modeled as a function of their potential revenue.

@@

Consider a user seeking to prevent
data overage by purchasing enough data from a subset of other network users.
This user $i$ can be modeled as a opt-out buyer where $\vs_i^j$ denotes the
fraction of user $j$'s data aquired by user $i$. (TAKE OUT: Buyer $i$ has an incentive to
to maximize the amount of requested data from one seller, thereby minimizing
the bid fee paid to the ISP and still fufill thier data requirement.)
For the sellers that do not meet a $i$'s data requirements, a rational (utility-maximizing) buyer will
set $s_i^j = 0$, i.e. they will not place a bid, as in \cite{zheng}. Also we
note that since $i$ is not a seller, $d_i^i = 0$ and $a^i = 0$.

@@

In order to form the distributed auction, we set $\vs_i^j=1$ for all sellers
who offer enough data to meet the needs required by buyer $i$, and $\vs_i^j=0$ for
all other $j$. This restricts the number of auctions in which the user is able to
participate. We intend to show that this does not affect thier valuation, and
indeed, in this network setting, results in a shared network optima (a
global optimum). The formulation is inversely analogous to the thinnest allocation route for
bandwidth given in \cite{lazar}. Reasonably, if only a single seller is available, then
(\ref{opt-out}) reduces to the original form (\ref{utility}), defined in
\cite{semret} as "a simple buyer at a single resource element".

The seller, in our analysis, is an extension of the buyer, where the valuation
$\theta^j$ is dependent on the buyers. The natural utility is the potential
profit from buyer $i$, $u^j = \theta^j\circ e_i(a)$, where $\theta^j$ is the
potential revenue from the sale of data composed with buyer $i$'s opt-out value
$e_i(a)$. We derive the potential revenue as a function of demand $\varrho$ as in
\cite{semret}, $\forall \ y\ge 0$, the demand for $j$ at unit price $y$ is given by
$$
    \varrho^j(y) \triangleq \displaystyle\sum_{p_j^i\ge y} d_j^i,
$$
with inverse
$$
    f^j(z) \triangleq \sup\big\lbrace y\ge 0: \varrho^j(y) \ge z\big\rbrace.
$$
Therefore, we have the seller's valuation \cite{semret}, 
$$
    \theta^j\circ e_i(a) = \displaystyle\int_0^{e_i(a)} f^j(z) \ dz.
$$
We note the difference in subscript/superscript notation from \cite{semret},
 we emphasize the separation of buyers and sellers, and our
claim that the seller's valuation depends on the opt-out \emph{buyer demand}.
The proof remains the same from \cite{semret}.

@@

Consider an opt-out buyer $i\in\mathcal{I}$, participating in many auctions
simultaneously. Due to (\ref{opt-out}), a seller only has an incentive to change its
bid value if it increases its expected opt-out value $e_i$. This creates an
incentive for $i$ to coordinate its bids to maximize (DOUBLE MAX? DOES THIS
MAKE SENSE?) the number of available sellers (with respect to the demand
threshold), and therefore maximize its overall
utitlity. We show that, without loss of utility, a buyer $i$ can increase its
bid quantities $d_i$ to the level where the opt-out value $e_i^j$ is the same
for each
\emph{qualifying} seller $j$. We show that buyer coordination \cite{semret} holds in the
secondary data market under our assumptions.
{
\lemma{(Opt-out buyer coordination)} Let $i\in\mathcal{I}$ be a opt-out buyer.
For any profile $s_i = (d_i, p_i)$, let $a \equiv a(s)$ be the resulting data
tranfer. For a fixed $s_{-i}$, a better reply for $i$ is $x_i =
(z_i,p_i)$ where $\forall \ l \ne i$,
$$
    z_i^l = \frac{\big\lbrack e_i(a) \big\rbrack}{\vs_i^l},
$$
and
\begin{equation}\label{coordination}
    a_i^l(z_i,p_i) = z_i^l.
\end{equation}
}
\textbf{Proof:} We will show that
\begin{equation}
    u_i(s_i;s_{-i}) \equiv u_i(d_i,p_i) \le u_i(z_i,p_i)
\end{equation}
using the modified allocation rule from \cite{tuffin} and our current
formulation. $\forall \ l \in \mathcal{I}$,
\begin{align}
\begin{split}
    z_i^l &= e_i(a)/\vs_i^l = \big[\max_{j\ne i} e_i^j(a)\big]/ \vs_i^l\\
    & \ge  e_i^j(a) = a_i^j\vs_i^j/\vs_i^l\\
    & \ge \frac{d_i}{\sum_{k:p_k=p_i} d_k}d_i(p_i;s_i) \\
    & = \frac{d_i}{\sum_{k:p_k=p_i} d_k}\bigg[D-\displaystyle\sum_{p_k>y,k\ne
i} d_k\bigg]^+.
\end{split}
\end{align}
Using the allocation (\ref{allocation}) rule again, we have
\begin{align*}
    a_i^l(z_i,p_i) &= \max\bigg(z_i^l, \\
\frac{d_i}{\sum_{k:p_k=p_i} d_k}&\bigg[D-\displaystyle\sum_{p_k>y,k\ne
i} d_k^l\bigg]^+\bigg) \\
    &= z_i \\
    &= e_i(a)\vs_i^l,
\end{align*}
and (\ref{coordination}) is proven. Then we have that $e_i(a(z_i,p_i)) =
a_i^l(z_i,p_i)\vs_i^l
= e_i(a) \ \forall \ l\ne i$, and so
$\theta_i\circ e_i(a(z_i, p_i)) = \theta_i\circ e_i(a)$. Now, by definition of
the seller's valuation, $\forall \ l$,
$$
    e_i(a) \ge e_i^l(a) \Rightarrow z_i^l\vs_i^l \ge a_i^l\vs_i^l \Rightarrow
a_i^l \le z_i^l\le a_i^l(z_i,p_i).
$$ 
Additionally, we comment that $x_i$ is feasible, i.e. $\sum_l c_i^l(s) \le b_i$
as the factor $\vs$ separates the auction space, restricting the number of bids
a user may place (SAY THIS BETTER!). In effect, we are using the buyer demand
to partition the auction space, thereby optimizing the message space for the
ISP, and providing an optimal market space to host the buyers and sellers based
on their type.
(....AND!?) 
The rest of the proof follows as in \cite{semret}.

The idea of buyer coordination follows from \cite{lazar} (FINISH!)

(DOES THIS PROOF EVEN CHANGE?)
{
\proposition{(Network incentive compatibility)}
Let $i\in\mathcal{I}$ be an opt-out buyer, and fix all other users' bids
$s_{-i}$, as well as the sellers' bids $s_i^i$ (so $a^i$ is fixed). \\
Let 
\begin{align}
    z_i &= \sup\bigg\lbrace h\ge 0 : \\
& \theta_i(h) > \displaystyle\sum_{j\ne i}
P_i^j\big((h-a_j^i)\vs_i^j\big)\vs^j\bigg\rbrace, 
\end{align}
\begin{align}\label{price}
    \psi_i &= \sup\bigg\lbrace h\ge 0: \\
&\displaystyle\int_0^h \displaystyle\sum_{j\ne i}
P_i^j\big((h-a_j^i)\vs_i^j\big)\vs^j \ dh \le b_i\bigg\rbrace,
\end{align}
$e = \max(z_i, \psi_i - \epsilon / \theta_i'(0))^+$, and for each $j\ne i$, 
$$
    v_i^j = (e - a_j^i)\vs_i^j
$$
and 
$$
    w_i^j = \vs_i^j\theta_i'(e).
$$
Then a (coordinated) $\epsilon$-best reply for the opt-out buyer is $t_i =
(v_i,w_i)$, i.e., $\forall \ s_i, u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;
s_{-i})$.
} \\ \\
\textbf{Proof:} First suppose $e = z_i$. Since $\theta_i'$ is non-increasing
and $\forall j$, $P_i^j$ is non-decreasing, \ref{price} implies $\theta_i'(e) >
\sum_{j\ne i} P_i^j(v_i^j)\vs_i^j$, and so $\forall j\ne i$,

>>>>

We extend the P2P rules as in \cite{semret} to include a \emph{local} market
price function as determined by the subset of nodes participating in the
auction. Therefore the influence of the greater market on the individual
auctions will be influenced only by the submission of bids from buyers to
sellers. As a buyer may have access to multiple auctions, the sellers will be
dynamically influenced by the $\epsilon$-best replies from the buyers. (need to
start to explain the opt-out buyer here... is the basis for network
equilibrium, as the optimal solution is to have the opt-out function the same
for all sellers i.e. P2P theory..).

@@

Consider a user seeking to prevent
data overage by purchasing enough data from a subset of other network users.
This user $i$ can be modeled as a opt-out buyer where $\vs_i^j$ denotes the
fraction of user $j$'s data aquired by user $i$. Buyer $i$ has an incentive to
to maximize the amount of requested data from one seller, thereby minimizing
the bid fee paid to the ISP and still fufill thier data requirement.
For the sellers that do not meet a competing buyer $k$'s data requirements, a rational (utility-maximizing) buyer will
set $s_k^j = 0$. We note that since $i$ is not a seller, $d_i^i = 0$ and $a^i = 0$.

@@

In order to form the distributed auction, we set $\vs_i^j=1$ for all sellers
who offer enough data to meet the needs required by buyer $i$, and $\vs_i^j=0$ for
all other $j$. This restricts the number of auctions in which the user is able to
participate. We intend to show that this does not affect thier valuation, and
indeed, in this network setting, results in
(EEEK! say something else like... results in a shared network optima, or a
global optimum.) the smallest
number of auctions that the network participates in as a whole (NOTE: can I
formulate this?), and is inversely analogous to the thinnest allocation route for
bandwidth given in \cite{lazar}. Reasonably, if only a single seller is available, then
(\ref{opt-out}) reduces to the original form (\ref{utility}), defined in
\cite{semret} as "a simple buyer at a single resource element".

The seller, in our analysis, is an extension of the buyer, where the valuation
$\theta^j$ is dependent on the buyers. The natural utility is the potential
profit from buyer $i$, $u^j = \theta^j\circ e_i(a)$, where $\theta^j$ is the
potential revenue from the sale of data composed with buyer $i$'s opt-out value
$e_i(a)$. We derive the potential revenue as a function of demand $\varrho$ as in
\cite{semret}, $\forall \ y\ge 0$, the demand for auction $j$ at unit price $y$ is given by
$$
    \varrho^j(y) \triangleq \displaystyle\sum_{p_j^i\ge y} d_j^i,
$$
with inverse
$$
    f^j(z) \triangleq \sup\big\lbrace y\ge 0: \varrho^j(y) \ge z\big\rbrace.
$$
Therefore, we have the seller's valuation \cite{semret},
$$
    \theta^j(x) = \displaystyle\int_0^x f^j(z) \ dz,
$$
and 
$$
    \theta^j\circ e_i(a) = \displaystyle\int_0^{e_i(a)} f^j(z) \ dz.
$$
We note the difference in subscript/superscript notation from \cite{semret},
 we emphasize the separation of buyers and sellers, and our
claim that the seller's valuation depends on the opt-out \emph{buyer demand}.
The proof remains the same from \cite{semret}.

@@

Consider an opt-out buyer $i\in\mathcal{I}$, participating in many auctions
simultaneously. Due to (\ref{opt-out}), data allocations are only valuable to the
seller if they decrease the expected matching of buyer $i$ (i.e. the buyer finds another
seller). This creates an incentive for $i$ to coordinate its bids
to maximize the number of available sellers, and therefore maximize its overall
utitlity. We show that, without loss of utility, a buyer $i$ can decrease its
bid quantities $d_i$ to the level where the opt-out value is the same for all
$j$ sellers. We show that buyer coordination \cite{semret} holds in the
secondary data market.
{
\lemma{(Opt-out buyer coordination)} Let $i\in\mathcal{I}$ be a opt-out buyer.
For any profile $s_i = (d_i, p_i)$, let $a \equiv a(s)$ be the resulting data
tranfer. For a fixed $s_{-i}$, a better reply for $i$ is $x_i =
(z_i,p_i)$ where $\forall \ j \ne i$,
$$
    z_i^j = \big\lbrack e_i(a) \big\rbrack,
$$
and
\begin{equation}\label{coordination}
    a_i^j(z_i,p_i) = z_i^j.
\end{equation}
}
\textbf{Proof:} We will show that
\begin{equation}
    u_i(s_i;s_{-i}) \equiv u_i(d_i,p_i) \le u_i(z_i,p_i)
\end{equation}
using the modified allocation rule from \cite{tuffin} and our current
formulation. $\forall \ j \in \mathcal{I}$,
\begin{align}
\begin{split}
    z_i^j &= e_i(a) = \max_{j\ne i} e_i^j(a)\\
    & \le  e_i^j(a) = a_i^j\vs_i^j\\
    & \le \frac{d_i}{\sum_{k:p_k=p_i} d_k}d_i(p_i;s_i) \\
    & = \frac{d_i}{\sum_{k:p_k=p_i} d_k}\bigg[D-\displaystyle\sum_{p_k>y,k\ne
i} d_k\bigg]^+.
\end{split}
\end{align}
Using the allocation rule again, we have
\begin{align*}
    a_i^j(z_i,p_i) &= \min\bigg(z_i^j, \\
\frac{d_i}{\sum_{k:p_k=p_i} d_k}&\bigg[D-\displaystyle\sum_{p_k>y,k\ne
i} d_k\bigg]^+\bigg),
\end{align*}
and (\ref{coordination}) is proven. We may now confirm that $e_i(a_i^j(z_i,p_i)) = a_i^j(z_i,p_i)
= z_i = e_i(a) \ \forall \ j\ne i$.
$\theta_i\circ e_i(a(z_i, p_i)) = e_i(a)$, 
{
\proposition{(Network incentive compatibility)}
Let $i\in\mathcal{I}$ be an opt-out buyer, and fix all other users' bids
$s_{-i}$, as well as the sellers' bids $s_i^i$ (so $a^i$ is fixed). \\
Let 
\begin{align}
    z_i &= \sup\bigg\lbrace h\ge 0 : \\
& \theta_i(h) > \displaystyle\sum_{j\ne i}
P_i^j\big((h-a_j^i)\vs_i^j\big)\sigma_i^j\bigg\rbrace, 
\end{align}
\begin{align}\label{price}
    \psi_i &= \sup\bigg\lbrace h\ge 0: \\
&\displaystyle\int_0^h \displaystyle\sum_{j\ne i}
P_i^j\big((h-a_j^i)\vs_i^j\big)\sigma_i^j \ dh \le b_i\bigg\rbrace,
\end{align}
$e = \max(z_i, \psi_i - \epsilon / \theta_i'(0))^+$, and for each $j\ne i$, 
$$
    v_i^j = (e - a_j^i)\vs_i^j
$$
and 
$$
    w_i^j = \vs_i^j\theta_i'(e).
$$
Then a (coordinated) $\epsilon$-best reply for the opt-out buyer is $t_i =
(v_i,w_i)$, i.e., $\forall \ s_i, u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;
s_{-i})$.
} \\ \\
\textbf{Proof:} First suppose $e = z_i$. Since $\theta_i'$ is non-increasing
and $\forall j$, $P_i^j$ is non-decreasing, \ref{price} implies $\theta_i'(e) >
\sum_{j\ne i} P_i^j(v_i^j)\vs_i^j$, and so $\forall j\ne i$,
